### 2020-02-11 frontmatter.tex
Shervin signed (no critiques). Re-read Chp 1.

Nästa fokus i avhandlingen är implementeringen av en minimal diskretelementsmörjnings-/kontaktdynamikmodell för simulering av täta partikelsuspensioner. Två huvudingredienser i modellen är (i) en referensram-invariant smörjmodell med kort räckvidd för sfäriska partiklar, och (ii) en stick/slip friktionskontaktmodell med mjuk kärna som aktiveras när partiklar överlappar varandra. Eftersom kontakt-växelverkningar dominerar fysikaliskt vid höga partikelkoncentrationer, förväntar vi oss att metodologin också är tillämplig för att undersöka inklämning av icke-sfäriska partiklar och reologi för skum.

>>>>

Nästa fokus i avhandlingen är implementeringen av en minimal diskret-elementsmörjnings-/kontaktdynamikmodell för simulering av täta partikelsuspensioner. Två huvudingredienser i modellen är (i) en referensram-invariant smörjmodell med kort räckvidd för sfäriska partiklar, och (ii) en stick/slip friktionskontaktmodell med mjuk kärna som aktiveras när partiklar överlappar varandra. Eftersom kontakt-växelverkningar dominerar fysikaliskt vid höga partikelkoncentrationer, förväntar vi oss att metodologin också är tillämplig för att undersöka inklämning av icke-sfäriska partiklar och reologi för skum.

### 2020-02-11 overview.tex
Shervin signed (no critiques). Re-read Chp 1.

Despite the theoretical promise, fabricating photonic crystals with 3D bandgaps remains a practical challenge in the colloidal community \citep{Velev_etal_AM2009, Sacanna_etal_COCIS2011, Shen_AS_2016}.
The issue is twofold.
On the one hand, ideal PhC has the structure of a diamond cubic, which can have up to 40\% bandgap opening \citep{PRL1990}.\footnote{The percentage corresponds to the portion of frequencies that propagation of light is forbidden.}
Therefore, for a long time, the holy grail for photonic researchers has been designing a protocol that can position colloidal droplets in a diamond cubic with alternating dielectric constants.
In practice, however, diamond crystals are extremely difficult to assemble because of the large gaps in between; specifically, a diamond cubic of equal spheres has at most 34\% packing fraction, while a face-centered cubic can reach 74\%. This makes PBG hard to achieve in 3D considering its sensitivity to structural defects.
On the other hand, even if one does aim for the diamond structure, current techniques relying on Brownian motions and ``patchy particles'' are too slow to build PhC in the range of visible light \citep{Yi_etal_CM2013}. In some sense, droplets assembled this way are assembled by chance, which favors anisotropic structures with a higher rotational entropy \citep{Meng2010}.
%such circuitry presents a great challenge as defects need to be carefully incorporated into the photonic-crystal structure with great precision. Although this has been accomplished for two-dimensional designs that confine light in a plane, it is still an ongoing challenge for so-called complete-bandgap materials, where the defects need to be embedded into a three-dimensional structure.

@@

\medskip
In partial response to the challenge, we numerically explore dense suspensions under different imposed flow conditions and geometric constraints.
In particular, we study particles in the noncolloidal regime, and ask:
(i) how to minimally characterise the microstructural evolution in an unsteady flow. Candidate answers include the complex viscosity, particle diffusivity, suspension fabric, size distribution of local clusters, structure factor, \etc \citep{Brady_Bossis1988, Sal03, Ness_Xing_Eiser_2017}.
(ii) Can qualitatively different global behaviours, such as a rate-dependent rheology vs.\ a rate-independent rheology, occur to the same suspension under different flow protocols (Ge \textit{et al.}, in preparation)? And
(iii) how does the particle geometry affect the rheology and jamming of a suspension at fixed volume fractions?
Solving these problems requires a numerical methodology that is accurate enough to test different physical hypotheses and efficient enough to generate data for a wide range of parameters. The implementation details of one such algorithm is documented in \emph{Paper 7}.

\thesisstructure
In the remaining of the thesis, we summarise previous studies in the literature to provide an extended overview on droplet interactions and suspension flow.
This is the \emph{Part I} of the thesis and contains four more chapters.
In Chapter \ref{chp:micro-hydro}, we formulate the equations governing the microhydrodynamics and
spotlight the essential physics for one, two and more particles in various flow fields or geometries.
These are the prerequisites for understanding droplet interactions in more complicated conditions.
In Chapter \ref{chp:num-methods}, we introduce two categories of numerical methodologies that
either solve the governing equations directly or approximate the solution in reduced order.
Each category is then divided into several classes, which have further variations and are mentioned succinctly.
These are followed by a short detour in Chapter \ref{chp:misc},
where two additional topics studied alongside the main subject are motivated and described.
Finally, Chapter \ref{chp:summary} concludes the first part of the thesis,
leading us to \emph{Part II}, where the original results are collected in the form of papers.

>>>>

Despite the theoretical promise, fabricating photonic crystals with 3D bandgaps remains a practical challenge in the colloidal community \citep{Velev_etal_AM2009, Sacanna_etal_COCIS2011, Shen_AS_2016}.
The issue is twofold.
On the one hand, ideal PhC has the structure of a diamond cubic, which can have up to 40\% bandgap opening \citep{PRL1990}.\footnote{The percentage corresponds to the portion of frequencies that propagation of light is forbidden.}
Therefore, for a long time, the holy grail for photonic researchers has been designing a protocol that can position colloidal droplets in a diamond lattice with alternating dielectric constants.
In practice, however, diamond crystals are extremely difficult to assemble because of the large gaps in between; specifically, a diamond cubic of equal spheres has at most 34\% packing fraction, while a face-centered cubic can reach 74\%. This makes PBG hard to achieve in 3D considering its sensitivity to structural defects.
On the other hand, even if one does aim for the diamond structure, current techniques relying on Brownian motions and ``patchy particles'' are too slow to build PhC in the range of visible light \citep{Yi_etal_CM2013}. In some sense, droplets assembled this way are assembled by chance, which favors anisotropic structures with a higher rotational entropy \citep{Meng2010}.
%such circuitry presents a great challenge as defects need to be carefully incorporated into the photonic-crystal structure with great precision. Although this has been accomplished for two-dimensional designs that confine light in a plane, it is still an ongoing challenge for so-called complete-bandgap materials, where the defects need to be embedded into a three-dimensional structure.

@@

\medskip
In partial response to the challenge, we numerically explore dense suspensions under different imposed flow conditions and geometric constraints.
In particular, we study particles in the noncolloidal regime, and ask:
(i) how to minimally characterise the microstructural evolution in an unsteady flow?
Candidate answers include the (complex) suspension viscosity, particle diffusivity, suspension fabric, size distribution of local hydroclusters, structure factor, \etc \citep{Brady_Bossis1988, Sal03, Ness_Xing_Eiser_2017}.
(ii) Can qualitatively different global behaviours, such as a rate-dependent rheology vs.\ a rate-independent rheology,
occur to the same suspension under different flow protocols? And
(iii) how does the particle geometry affect the rheology and jamming of a suspension at fixed volume fractions?
Solving these problems requires a numerical methodology that is accurate enough to test different physical hypotheses and
efficient enough to generate data for a wide range of parameters.
The implementation details of one such algorithm is documented in \emph{Paper 7}.

\thesisstructure
In the remaining of the thesis, we summarise previous studies in the literature to provide an extended overview on droplet interactions and suspension flow.
This is the \emph{Part I} of the thesis and contains four more chapters.
In Chapter \ref{chp:micro-hydro}, we formulate the equations governing the microhydrodynamics and
spotlight the essential physics for one, two and more particles in various flow fields or geometries.
They are the prerequisites for understanding droplet interactions in more complicated conditions.
In Chapter \ref{chp:num-methods}, we introduce two categories of numerical methodologies that
either solve the governing equations directly or approximate the solution in reduced order.
Specifically, each category is divided into several classes, which have further variations and are mentioned succinctly.
These are followed by a short detour in Chapter \ref{chp:misc},
where two additional topics studied alongside the main subject are motivated and described.
Finally, Chapter \ref{chp:summary} concludes the first part of the thesis,
leading us to \emph{Part II}, where the original results are collected in the form of papers.

### 2020-02-11 paper1/article.tex
Shervin signed (no critiques). Re-read Chp 1.

In the field of colloidal science, much progress has been made on the synthesis of elementary building blocks \Ge{(Fig.\ \ref{fig:exp})} mimicking molecular structures to elaborate innovative materials, \eg materials with complete three dimensional band gaps \citep{Xia_etal_AM2000, Velev_etal_AM2009, Li_etal_AC2011, Sacanna_etal_COCIS2011}. The basic elements of such colloidal molecules are particles or droplets less than one millimeter in size, and their self-assembly relies on either lengthy brownian motion or careful microfludic designs, on top of typical colloidal interactions, \eg depletion attraction and electrostatic repulsion \citep{Mewis_colloidal, Yi_etal_CM2013, Shen_AS_2016}. Regardless of the approach, however, questions remain why the colloidal particles/droplets undergo certain path to organize themselves and how such process can be controlled and optimized. Since full data are not yet accurately accessible from experiments in such miniature systems, computer simulations will be useful to provide supplemental information.

>>>>

In the field of colloidal science, much progress has been made on the synthesis of elementary building blocks \Ge{(Fig.\ \ref{fig:exp})} mimicking molecular structures to elaborate innovative materials, \eg materials with complete three dimensional band gaps \citep{Xia_etal_AM2000, Velev_etal_AM2009, Li_etal_AC2011, Sacanna_etal_COCIS2011}. The basic elements of such colloidal molecules are particles or droplets less than one millimeter in size, and their self-assembly relies on either lengthy Brownian motion or careful microfludic designs, on top of typical colloidal interactions, \eg depletion attraction and electrostatic repulsion \citep{Mewis_colloidal, Yi_etal_CM2013, Shen_AS_2016}. Regardless of the approach, however, questions remain why the colloidal particles/droplets undergo certain path to organize themselves and how such process can be controlled and optimized. Since full data are not yet accurately accessible from experiments in such miniature systems, computer simulations will be useful to provide supplemental information.

### 2020-02-11 paper4/article.tex
Shervin signed (no critiques). Re-read Chp 1.

We use interface-resolved, direct numerical simulations to obtain motions of the particles and full solutions of the ambient flow field. The particles are simulated either as solid spheres using an immersed boundary method or as liquid droplets using the interface-correction level set/ghost fluid method; see \cite{ibm,icls,flow-assist} and the Appendix B of \cite{Fouxon_2017} for detailed descriptions of the governing equations and their numerical treatments. Note that, our solvers does not neglect any details (up to the numerical precision) of the fluid motion throughout a suspension, hence it is better suited for detailed studies of few hydrodynamically interacting particles despite being computationally more expansive, cf.\ \cite{Swan_Brady_2007}.

>>>>

We use interface-resolved, direct numerical simulations to obtain motions of the particles and full solutions of the ambient flow field. The particles are simulated either as solid spheres using an immersed boundary method or as liquid droplets using the interface-correction level set/ghost fluid method; see \cite{ibm,icls,flow-assist} and the Appendix B of \cite{Fouxon_2017} for detailed descriptions of the governing equations and their numerical treatments. Note that, our solvers does not neglect any details (up to the numerical precision) of the fluid motion throughout a suspension, hence it is better suited for detailed studies of few hydrodynamically interacting particles despite being computationally more expensive, cf.\ \cite{Swan_Brady_2007}.

### 2020-02-11 paper7/paper.tex
Shervin signed (no critiques). Re-read Chp 1.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of DLCD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal discrete-\\element lubrication/contact dynamics model \\for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense \\suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, Department of Engineering Mechanics,\\
  KTH Royal Institute of Technology, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{2020}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal discrete-element lubrication/contact dynamics (DLCD) model
   intended for simulation of dense particle suspensions in shear flows.
   The method is meshless, explicit and solves directly the particle dynamics in the overdamped limit
   by balancing conservative and dissipative interactions at the pair level.
   Potential limitations include omissions of fluid/particle inertia and long-range hydrodynamic interactions.
   The implementation has been tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%,
   showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of DLCD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense \\suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, Department of Engineering Mechanics,\\
  KTH Royal Institute of Technology, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{2020}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal discrete-element lubrication/contact dynamics (DLCD) model
   intended for simulation of dense particle suspensions in shear flows.
   The method is meshless, explicit and solves directly the particle dynamics in the overdamped limit
   by balancing conservative and dissipative interactions at the pair level.
   Potential limitations include omissions of fluid/particle inertia and long-range hydrodynamic interactions.
   The implementation has been tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%,
   showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}
